### 2017-04-01 thesis/latex/thesis.tex
Thesis: finish attn grabber.

@@

Mention the Burgess paper, which says spring constants might change between apo/ADP states.

>>>>

\subsection{Interest builder}
Motor proteins are cellular structures which use chemical energy to do work and generate motion. Kinesin, myosin and dynein are the three main motor proteins in cells. Though these proteins have significantly different ancestors [cite], they all evolved into a single similar structure. In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way for solving a problem. How, then, do motor proteins work?\\

The basic form is simple. Kinesin, myosin and dynein each use two binding domains to attach to a surface. These binding domains are connected via a linker domain. Each motor protein is an engine which undergoes cycles, where each cycle moves the motor across a surface. In a single cycle a binding domain will unbind from a surface, tense its foot to kick forward, rebind, then untense its foot to pull the whole motor forward. This pattern is repeated by both feet to generate motion \cite{kinesin-cycle} \cite{myosin-cycle}.\\

Although the three motor protein families operate using the same stepping cycle, their behavior differs significantly. Kinesin and myosin are predictable motors which step in the forwards direction with a regular step size [get kinesin, myosin stepping papers]. In contrast, dynein's stepping pattern varies wildly in both size and direction. The motor steps forward on average, but takes steps backwards and to the side quite regularly \cite{weihongpaper}. How can motors which implement the same release, lever, bind, lurch stepping mechanism behave so differently?\\

One possibility is that dynein's size and organization are responsible for the motor's odd stepping pattern. Dynein is much larger than kinesin or myosin, meaning its feet may need to move significantly further over each cycle. Due to the random nature of Brownian motion from water particle collisions, there may be significantly more variance in the path taken by dynein's feet compared to other motor feet. This could explain the large variance in step size. Another contributing factor could be that dynein is so large that it can twist and contort during its step, allowing varying and even backwards steps, which a small motor would be too tense to achieve.\\

This thesis aims to test whether Brownian motion and flexibility are what give rise to dynein's unique stepping pattern. To do this, an artificial motor model is created which exhibits flexibility and is affected by Brownian motion. This model is then simulated, and its behavior are compared to the behavior of real dynein.

%% Dynein:
%% feet which bind to track
%% motor connected to feet which generates the force
%% -----------
%% ATP binding causes dissociation
%% Also causes forward kick
%% ATP hydrolysis
%% rebinding causes ADP rejection and forward lurch
%% restart

%% Kinesin:
%% feet which bind to track
%% connected via lever arm to cargo binding domain
%% -----------
%% ATP binding causes forward kick
%% ATP hydrolysis
%% MT binding, ADP, Pi rejection
%% Other foot unbinds

%% Myosin:
%% Feet which bind to track
%% connected via lever arm to cargo binding domain
%% ----------
%% actin binding causes Pi rejection, strengthening binding
%% binding causes foot to change relative to lever, shifting the motor forward
%% ATP binding causes dissocaition and undoing the powerstroke

@@

Mention the Burgess paper, which says spring constants might change between apo/ADP states.
Also dynein may move helically: Bidirectional helical motility of cytoplasmic dynein around microtubules
